---
title: "README"
author: "Dr. Elizabeth Bowman"
date: "6/28/2021"
output: html_document
---
The folders here contain R scripts and data files for the article "Evidence of plant-soil feedback in South Texas grasslands associated with invasive Guinea grass independent of soil inoculation method " written by Elizabeth A. Bowman, Robert M. Plowes, and Lawrence E. Gilbert

Elizabeth A. Bowman is the author for correspondence on this article. 
Address: 
Brackenridge Field Laboratory
Room 105
2907 Lake Austin Blvd.
Austin, TX 78703
United States

Elizabeth A. Bowman wrote all scripts for data analysis.
Email: eabowman@utexas.edu

------------------------------------------------------------------------------------------

Explanation of folders:
1. The data folder contains all data files used in the R script for analyses with
explanations of columns.
2. The figure folder is an output folder where figures generated in the R script will be
output.
3. The results folder is an output folder for results tables generated in the R script.
4. The script folder contains all scripts organized by type of analysis.

Each of these folders contains a 'Read me' file with further explanations.

------------------------------------------------------------------------------------------

The following code will run each analysis and output figures and result tables to their
appropriate folders.

# Load file paths

```{r file paths}
#--file path to data directory
dat.dir <- 'data/'
fig.dir <- 'figures/'
res.dir <- 'results/'
script.dir <- 'script/'
```

# Load packages  

If you need to install packages, open 'Load_packages.R' and uncomment 'install.packages'
before running. 

```{r libraries}
source(paste0(script.dir, "LoadLibraries.R"))
```

# Plant-soil feedback effect on Guinea grass
The results from these analyses are shown in Table II. The plots are from
Fig. I and Fig. IIIA.

```{r Effect on Guinea Grass growth}
source(paste0(script.dir, "AnalysisGuineaGrass.R"))
```

# Plant-soil feedback effect on the native seed bank
The results from these analyses are shown in Table III. The plots are from
Fig. II, Fig. IIIB, and Fig. IIIC.


```{r Effect on growth of the native seedbank}
source(paste0(script.dir, "AnalysisNativeCommunity.R"))
```

# Analysis of soil data
Effect of autoclaving on soil characteristics and differences in soil 
characteristics as a function of invasion.

Output from AnalysisAutoclaveEffect.R is Supplementary Table SI.
Output from AnalysisSoil.R is Supplementary Figure SII

```{r Soil data}
# Autoclaving
source(paste0(script.dir, "AnalysisAutoclaveEffect.R"))

# Soil as a function of invasion
source(paste0(script.dir, "AnalysisSoil.R"))
```
